---
title: "WC_cluster_slides"
author: "Alexis"
date: "13/02/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)

#heatmaps
events <- read_csv(here::here("data/events.csv"))


circleFun <- function(center = c(0,0),diameter = 1, npoints = 100){
  r = diameter / 2
  tt <- seq(0,2*pi,length.out = npoints)
  xx <- center[1] + r * cos(tt)
  yy <- center[2] + r * sin(tt)
  return(data.frame(x = xx, y = yy))
}

pen_spot_1 <- c(12,40)
pen_spot_2 <- c(108,40)
center <- c(60,40)
#### create leftD arc ####
Dleft <- circleFun(pen_spot_1, diameter = 20, 1000)
Dleft <- Dleft[which(Dleft$x > 18),]

points <- rbind(pen_spot_1, pen_spot_2, center)

#### create rightD arc ####
Dright <- circleFun(pen_spot_2, diameter = 20, 1000)
Dright <- Dright[which(Dright$x < 102),]

### create center ###
center_circle <- circleFun(center, diameter = 20, 1000)


plot_heatmaps <- function(data, cluster_nb) {
  
  data <- data %>% filter(cluster == cluster_nb)
  
  ggplot(data, aes(x = location.x, y = location.y)) +
    geom_bin2d(binwidth = c(10,10)) +
    scale_fill_distiller(palette = "RdYlGn", guide = FALSE) +
    annotate("rect", xmin = 0, xmax = 120, ymin = 0, ymax = 80,
             fill = "transparent",
             color = "black") + #terrain
    annotate("rect", xmin = 0, xmax = 18, ymin = 18, ymax = 62,
             fill = "transparent",
             color = "black") + #surface
    annotate("rect", xmin = 0, xmax = 6, ymin = 30, ymax = 50,
             fill = "transparent",
             color = "black") + #6m
    annotate("rect", xmin = 0, xmax = -2, ymin = 36, ymax = 44,
             fill = "transparent",
             color = "black") + #but
    annotate("rect", xmin = 102, xmax = 120, ymin = 18, ymax = 62,
             fill = "transparent",
             color = "black") + #surface
    annotate("rect", xmin = 114, xmax = 120, ymin = 30, ymax = 50,
             fill = "transparent",
             color = "black") + #6m
    annotate("rect", xmin = 120, xmax = 122, ymin = 36, ymax = 44,
             fill = "transparent",
             color = "black") + #but
    annotate("segment", x = 60, xend = 60, y = 0, yend = 80) +
    annotate("path", x = Dleft$x, y = Dleft$y) + #Dleft
    annotate("path", x = Dright$x, y = Dright$y) + #Dright
    annotate("path", x = center_circle$x, y = center_circle$y) + #Center circle +
    annotate("point", x = points[,1], y = points[,2]) +
    coord_flip() +
    theme_void() +
    theme(aspect.ratio = 3/2)
}

plots_heatmap <- 1:6 %>%
  map(~plot_heatmaps(events, .x))


library(ggtern)

#ternary plots
profile <- read_csv(here::here("data/events_sum.csv"))
profile$cluster <- as.factor(profile$cluster)

all_clusters <- ggtern(data = profile, aes(x = prop.Pass, y = prop.Shot, z = prop.Dribble,
                                           fill = cluster)) +
  geom_point(size = 2,
             shape = 21) +
  tern_limits(T= 0.3, L = 1, R = 0.3) +
  labs(xarrow = "Passes",
       yarrow = "Tirs",
       zarrow = "Dribbles") +
  theme_bw() +
  theme_arrowdefault() +
  theme(tern.axis.title.show = FALSE) +
  scale_fill_brewer(palette = "Dark2")


plot_cluster <- function(data, cluster_nb) {
  color <- RColorBrewer::brewer.pal(6, "Dark2")[[cluster_nb]]
  
  data <- data %>% mutate(highlight = ifelse(cluster == cluster_nb, TRUE, FALSE))
  
  plot <- ggtern(data = data, aes(x = prop.Pass, y = prop.Shot, z = prop.Dribble,
                             fill = highlight)) +
    scale_fill_manual(values = c("grey70", RColorBrewer::brewer.pal(6, "Dark2")[[cluster_nb]]),
                      guide = FALSE) +
    geom_point(size = 2,
               shape = 21) +
    tern_limits(T= 0.3, L = 1, R = 0.3) +
    labs(xarrow = "Passes",
         yarrow = "Tirs",
         zarrow = "Dribbles",
         title = element_blank()) +
    theme_bw() +
    theme_arrowdefault() +
    theme(tern.axis.title.show = FALSE)
  
  return(plot)
}

plots_tern <- 1:6 %>%
  map(~plot_cluster(profile, .x))


```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Cluster 1

```{r cars, echo = TRUE}
plots_heatmap[1]
plots_tern[1]

```

## Slide with Plot

```{r pressure}
plot(pressure)
```

